SubsidyExplorer - Step 6: Run Model

### 2020-09-11 scripts/04_model_parameterization.Rmd

We assume $\phi = 1.188$ based on literature for all (Thorson et al. 2012; World Bank 2017; Costello et al. 2016).

>>>>

We assume $\phi = 0.188$ based on literature for all (Thorson et al. 2012; World Bank 2017; Costello et al. 2016).

> Thorson, J. T., Cope, J. M., Branch, T. A., & Jensen, O. P. (2012). Spawning biomass reference points for exploited marine fishes, incorporating taxonomic and body size information. Canadian Journal of Fisheries and Aquatic Sciences, 69(9), 1556–1568. https://doi.org/10.1139/f2012-077

### 2020-09-11 scripts/07_sensitivity_analysis.Rmd

title: "SubsidyExplorer - Step 7: Sensitivity Analysis"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

@@

## Relative subsidy effects

```{r}
# Vessel list with "effective" subsidies
### Not applicable currently - old experimentation with pro-rating the dollar value of different subsidies
# if(pro_rate_subsidies == T){
# 
#   vessel_dat <- vessel_dat %>%
#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
# 
# }
```

## Bioeconomic model parameters

>>>>

title: "SubsidyExplorer - Step 6: Run Model"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

# Introduction

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

@@

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))

# Source plotting script
source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
```

@@

```{r}
# Load biological parameters for the model
bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv"))

# Regional parameter list
bio_dat_regional_list <- bio_dat_regional %>%
  gather(region, value, -c(1:2)) %>%
  group_by(region) %>%
  group_split()
```

```{r}
# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.66
```

## Alternative model parameters
